---
title: "HM 06 Extra"
author: "Jiantong (Isabelle) Zhang"
format: html
embed-resources: true
editor: visual
---

```{r}
library(tidyverse)
library(moderndive)
theme_set(theme_minimal())
```

```{r}
data(bikes, package = "bayesrules")
glimpse(bikes)
```

## Question 0

There are 500 rows, each row represent a separate line of data. This dataset includes the date, season, year, month, day of week, whether it is weekend, whether it is holiday, the actual temperature, the temperature feeling, the humidity, the weather category, and the number of rides. The highest number of rides is 6946, and highest wind speed recorded is 34.

## Question 1

```{r}
cor_temp <- cor(bikes$rides, bikes$temp_feel)
cor_temp
```

The correlation is 0.58, which means the relationship between number of rides and what the temperature feels like (in Fahrenheit) is a moderate positive relationship. As the temperature (in Fahrenheit) increases, the number of rides tends to increase.

```{r}
cor_wind <- cor(bikes$rides, bikes$windspeed)
cor_wind
```

The correlation is 0.19, which means there is a weak negative linear relationship between the number of rides and wind speed. When the wind speed (in miles per hour) is higher, the number of rides tends to be lower. However, the correlation is pretty weak, meaning that the relationship is not very strong,

## Question 2

```{r}
library(dplyr)
bikes <- bikes |>
  mutate(wind_kph = windspeed *1.61)
glimpse(bikes)
```

```{r}
cor_kph_mph <- cor(bikes$windspeed, bikes$wind_kph)
cor_kph_mph
```

The correlation is one. A correlation of 1 means that the 2 variables are in perfect linear relationship, as one increases, the other increases in linear fashion. The windspeed kph and mph has a correlation of 1 because when we created windspeed kph, we created a linear transformation of the same underlying data, with each value in "wind_kph" being 1.61 times the corresponding value in "wind_mph."

## Question 3

```{r}
rides_mph <- lm( rides ~ windspeed, data= bikes)
broom :: tidy (rides_mph)|>
  select(term, estimate)
```

```{r}
rides_kph <- lm(rides ~wind_kph , data= bikes)
broom ::tidy(rides_kph) |>
  select(term, estimate)
```

The intercept for the two models are the same. The intercept represents the prediction value of rides when wind speed is zero, in both models, when there is no wind (0mph or 0kph), the numder of rides is the same.

The slope for model mph is 1.6 times the slope for model kph, this is because mph and kph is the linear transformation of the same underlying data, and one mile equals 1.6 kilometers. To align these slopes for comparison, the MPH slope is 1.6 times larger than the KPH slope, accounting for the unit conversion from miles to kilometers.

## Question 4

```{r}
library(ggeffects)
predictions <- ggpredict (rides_kph,
                          wind_kph = "20",
                          ci_level = NA)
predictions
```

If the wind is blowing at 20 kph, the predicted ridership is 3515.34.

```{r}
predictions <- ggpredict (rides_mph,
                          windspeed = "20",
                          ci_level = NA)
predictions
```

If the wind is blowing at 20 MPH, the predicted rides is 3094.61.

## Question 5

```{r}
bikes <- bikes |>
  mutate(temp_c = (temp_feel -32) * 5/9)
```

```{r}
mod1 <- 
  lm(rides ~ wind_kph + temp_c, data= bikes) 
  broom ::tidy(mod1) |>
  select(term, estimate)
```

For a 1 unit increase in wind_kph, the model expects a 19.84 decrease in number of rides. For a 1 unit increase in temp_c, the model expects a 143.23 increase in number of rides.

The intercept is 942.42, it means that when the wind_kph is zero and the temp_c is zero, the predicted number of rides is 942.42.

## Question 6

```{r}
pred_df <- tibble(
  situation = 1:3,
  temp_c = c(25, 15, 10),
  wind_kph = c(15, 5, 40))

pred_df <- pred_df |>
  mutate(predicted_ridership= predict (mod1, newdata = data.frame(temp_c, wind_kph)))
print(pred_df)
```

## Question 7 

```{r}
bikes <- bikes |>
  mutate (weekend = as.factor(weekend))

mod2 <- 
  lm(rides ~ wind_kph +temp_c +weekend, data= bikes)
broom ::tidy(mod2) |>
select(term, estimate)
```

The weekend coefficient has an estimate of -713.58, this means that with everything else being equal, on weekends, the model predicts a significant decrease of 713.58 rides compared to in weekdays.

## Question 8

```{r}
pred_df <- tibble(
  situation = 1:2,
  temp_c = c(mean(bikes$temp_c), mean(bikes$temp_c)),
  wind_kph = c(mean(bikes$wind_kph), mean(bikes$wind_kph)),
  weekend = c("TRUE","FALSE"))
pred_df <- pred_df |>
  mutate(predicted_ridership = predict(mod2, newdata= data.frame(temp_c, wind_kph, weekend)))
print(pred_df)
```

The expected ridership for a weekday is 3683.442, for a weekend is 2969.867.

## Question 9

```{r}
predicted_rides <- predict(mod2, newdata= bikes)

residuals <- predicted_rides - bikes$rides

bikes$residuals <- residuals

bikes <- bikes |>
  arrange(desc(abs(residuals)))

glimpse(bikes)
```

The highest residual is 3490.35. The date is 2012.10.29. Learning from Ethan and from further research, on October 29th, 2012, Hurricane Sandy hit the U.S. East Coast. Therefore, only 20 bike rides took place in Washington DC. This low ridership can be attributed to the extensive shutdown and preparations for the impending storm, which significantly disrupted normal activities in the region. And this might be why the prediction is so wrong.
