---
title: "Homework dv05"
author: "Jiantong Zhang"
embed-resources: true
format: html
editor: visual
---

```{r}
library(tidyverse)
wncaa <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/wncaa.csv")
glimpse(wncaa)
```

## Question 1

```{r}
wncaa_new <- wncaa |>
  filter(tourney_finish == "Champ") |>
  group_by(school) |>
  summarize(N = n()) |>
  mutate(freq = N / sum(N))

wncaa_new
```

```{r}
ggplot(data=wncaa_new, 
       mapping = aes(x= school, y= freq)) +
  geom_bar(stat= 'identity') +
  coord_flip()
```

Most schools won around 2.5-5% of tournaments. Uconn and Tennessee won the most tournaments, with Uconn winning nearly 30% and Tennessee winning over 20%.

## Question 2

```{r}
champs <- wncaa |>
  filter(tourney_finish == "Champ")
champ_names <- unique(champs$school)

```

```{r}
winners <- wncaa |>
  filter(school %in% champ_names)
```

```{r}
ggplot(data= winners,
       mapping= aes(x= school, y= seed))+
  geom_boxplot()+
  coord_flip()
```

```{r}
ggplot(data= winners,
       mapping= aes(x= school, y= seed))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter()+
  coord_flip()
```

```{r}
ggplot(data= winners,
       mapping= aes(x= reorder(school, seed), y= seed))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter()+
  coord_flip()
```

All of the 25%-75% distributions are within the 1 and 8 seed range, but the distributions vary by school. Most of the outliers are within the 0-2.5 seed range, many are in the 2.5-6 seed range, and there are some within the 6-12.5 seed range. Almost each school has outliers within the the 0-2.5 seed range. Although its distribution of seed is the 8th high, Louisiana tech has a highest outlier at around the 15 seed range.

```{r}
ggplot(data= winners,
       mapping= aes(x= reorder(school, seed), y= seed))+
  geom_violin(outlier.shape = NA)+
  geom_jitter()+
  coord_flip()
```

In this case, the first plot (boxplot) is more informative, because we can see the distribution very clearly, including where is the 25%, what is the 50%, and where is the 75% of each school.

## Question 3

```{r}
ggplot(data= winners,
       mapping= aes(x= reorder(school, seed), y= seed))+
  geom_point(alpha = 0.5) +
  coord_flip()
```

This plot does not work well because geom point is not aggregated data but is a scatter plot of separate points, and it can be hard to analyze the overall distributions in this plot.

## Question 4

```{r}
winners_mean_sd <- winners |> 
  group_by(school) |> 
  summarize(across(where(is.numeric),
                   list(mean = mean,
                        sd = sd)))
```

```{r}
ggplot(data=winners_mean_sd,
       mapping = aes(x= reorder(school, reg_percent_mean), y=reg_percent_mean )) +
  geom_point() +
  coord_flip()
```

All the teams have relatively high average winning percentage of over 74%. Texas A & M has the lowest regular season winning percentage of around 74%.

```{r}
ggplot(data= winners_mean_sd, 
       mapping= aes(x = reorder(school, reg_percent_mean), y = reg_percent_mean)) +
  geom_pointrange(aes(ymin = reg_percent_mean - reg_percent_sd, ymax = reg_percent_mean + reg_percent_sd)) +
  coord_flip() 

```

The school with the narrowest interval is Texas A&M, it means that this school has a smaller spread in average win percentages, and it's performance is relatively consistent.

```{r}
ggplot(data= winners_mean_sd, 
       mapping= aes(x = reorder(school, reg_percent_mean), y = reg_percent_mean)) +
  geom_linerange(aes(ymin = reg_percent_mean - reg_percent_sd, ymax = reg_percent_mean + reg_percent_sd)) +
  coord_flip() 
```

I think geom_pointrange is better, as it shows both the mean (the point at the center) and the distribution of a dataset, instead of only the distribution in geom_lineage. It allows us to know both the central tendency and the spread of data.
