---
title: "Homework chapter 06"
author: "Jiantong (Isabelle) Zhang"
embed-resources: true
format: html
editor: visual
---

```{r}
library(tidyverse)
library(moderndive)
library(broom)

theme_set(theme_light())

gender_employment <- read_csv('/Users/isabelle/Desktop/Data Analytics/soc223/gender_employment.csv')


glimpse(gender_employment)
```

```{r}
gender_employment|>
  ggplot(aes(x = year, y = wage_percent_of_male)) +
  geom_jitter(alpha = 0.1) + 
  geom_smooth(method = "lm") + 
  labs(title = "Women's earnings with respect to men's", 
       y = "% of Men's Income", 
       x = "Year")
```

## Question 1

```{r}
gender_employment <- gender_employment %>% 
  mutate(major_category = as.factor(major_category), 
         major_category = relevel(major_category, ref = "Management, Business, and Financial"))
```

```{r}
parallel_model <- lm(wage_percent_of_male ~ year + major_category, data= gender_employment)
```

```{r}
broom :: tidy(parallel_model)
```

The year estimate is 0.1922. This shows that there is a positive trend in the "wage_percent_of_male" over time. In other words, it suggests that, on average, the women's wage percentage of males is increasing by approximately 0.1922 units each year when other factors (including major_category) remain constant.

The wage percentage of male income for Sales and Office occupations on 2015 is

```{r}
-306.718 + 0.192*2015 +3.326 *1
```

The wage percentage of male income for Service occupations on 2016 is

```{r}
-306.718 + 0.192*2016 + 6.077 *1
```

## Question 2

```{r}
ggplot(data= parallel_model,
       mapping = aes(x= year,
                     y= wage_percent_of_male,
                     group =major_category)) +
  geom_parallel_slopes(se = FALSE)
```

I realize that all the lines are parallel. This is not a good assumption, as in this prediction, each category has the same slope, which might not have been closest to reality.

## Question 3

```{r}
parallel_model_2 <- lm(wage_percent_of_male ~ year + major_category + year: major_category, data= gender_employment)
```

```{r}
broom :: tidy(parallel_model_2)
```

The estimate for "Computer, Engineering, and Science" for 2016 is

```{r}
-1370.472 + 0.72 * 2016 + 1002.853 *1 -0.495*2016 *1
```

The estimate for service for 2016 is

```{r}
-1370.472 + 0.72 *2016 + 2137.650*1 -1.058 *2016 *1
```

The major category and the year : major category is different for the two categories, the prediction is more accurate than the previous model because we get to include year : major category. This model no longer predicts parallel trends.

## Question 4

Probably when we have way too many categories, if we have models that predicts parallel trends, it would be more simple to read and interpret.

## Question 5

```{r}
simple_fit <- lm(wage_percent_of_male ~ year, data= gender_employment)
```

```{r}
broom :: tidy(simple_fit)
```

The intercept is -321.832 and the slope is 0.201. If we want to predict the wage_percentage_of_male by year, the formula is wage_percentage_of_male = -321.832 + 0.201 \* year

```{r}
gender_employment |>
  select(year, wage_percent_of_male, percent_female) |>
  cor(use = "complete.obs")
```

The correlation between wage percent of male and year is 0.024, which suggests a very week positive relationship between them. The correlation between wage percent of male and percent female is 0.111, which is still pretty week positive relationship, but a little stronger than the previous one. The relationship between year and percent female is 0.005, which is close to 0, and indicates a very very very week positive relationship between the two variables.

```{r}
multiple_fit <- lm(wage_percent_of_male ~ year * percent_female, data= gender_employment)
broom :: tidy(multiple_fit)
```

The intercept is -800. The coefficient for year is approximately 0.438, which means that for each additional year, the wage percent of male increases by approximately 0.438 units. The coefficient for percent_female is approximately 10.64, which means that for each one-unit increase in the proportion of females working in an occupation, the wage percent of male increases by approximately 10.64 units. The coefficient for year: percent_female is -0.00526, which means there is a negative relationship: when the percentage of female rises, the positive relationship between year and wage percentage of male becomes weaker.

This is not exactly what I imagined: the first two coefficients fit my assumption, as I think that as the year rises, gender equality is promoted better, and that women would have a higher percentage of wage as compared to male, which fits the positive relationship. In addition, I also thought that when a job has higher percentage of female, the females are likely to have better chances of having a higher percentage of wage of male. However, I didn't expect the year: percent_female estimate to be negative, I thought that as the percentage of female rises, the positive relationship between year and wage percentage of male will become higher.

## Question 6

R-squared is a statistical measure that quantifies the proportion of the variation in the dependent variable. It is usually between 0 and 1. When a R-squared value closer to 1, it indicates that a larger proportion of the variation in the dependent variable can be attributed to the independent variable, and when it's closer to 0, vice versa.

```{r}
simple_glanced <- glance(simple_fit)
```

```{r}
simple_glanced $ r.squared
```

```{r}
multiple_glanced <- glance(multiple_fit)
```

```{r}
multiple_glanced $r.squared
```

For simple fit, the R square is very close to zero, which means that the variation of the wage_percent_of_male is nearly independent from year. For multiple fit, the R square is a little higher, but still only 0.01, this shows that only around 1% of the variation on the wage percent of male is dependent on the year, percentage female, and their interactions. This also shows a very weak dependent relationship.

## Extra 

```{r}
random_numbers <- rnorm(n = nrow(gender_employment), 
                        mean = 0, 
                        sd = 4)
```

```{r}
gender_employment$random_noise <- random_numbers

random_fit <- lm(wage_percent_of_male ~ year + percent_female + random_noise, data = gender_employment)

```

```{r}
random_glanced <- glance(random_fit)
```

```{r}
random_glanced $r.squared
```

This shows that even by adding a completely random variable, the R squared increased a bit. It shows the weakness of R square of improving whenever I add a variable, whatever that is.
